---
title: "Git and Github tutorial"
author: "James Lin"
date: "5/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

URL of github

*https://github.com/nilsemaj/test-repo*

# How to use git and github with R

*https://www.youtube.com/watch?v=QLFc9gw_Hfs*

1. Download Git from *https://git-scm.com/downloads*

2. Create an account with github at *https://github.com/*

3. Create a new repository

4. Copy `repository source URL

5. Click file, new project, version control, Git

6. Paste `repository source URL` into Repository URL input bar

  - save in a proper folder 

7. Can not make edits and work on different files

8. Click save 

9. In Git tab of the Enivornment, History, and Connections upper right panel, select the check boxes 

10. Click commit and write a commit comment

  - commit only gets a snap shot of saved files
  
11. Click push to send the saved files to Github

  - push sends the data files commited to github for cloud storage

```{r}

```



